Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-08 thesis/paper.tex
concl comments

Summarise the findings of the discussion
Summarise what the next steps could be.

Look up the papers from the conference (especially regarding the discussion/conclusion)
discussion = revisiting research questions (and maybe structuring around industry/academia)
conclusion = summary part, main final points and future work

Stuff for the conclusion:
Have a more structured feedback loop (include users) this can be future work too
Include more scientific theories

For future studies, this technique could be improved by performing more actions along side the code review. For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed. %%Conclusion stuff /Willy

%%The following should probably be in conclusion, right? /Willy
       What this means for industry:
              Greater emphasis should be placed upon communicating with the end users / application developers. APIs should be made with maintainability and extensibility in mind as they seem to be what changes the most between versions. They should probably improve their feedback system to get more feedback from the API users.

              Interesting that hardware did not drive change. Could be studied further in a new study to see if this applies to platform specific APIs in general?

              Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.

       What this means for academia:
              Academia could benefit from the results as a means for further research - We have found that it's possible to reverse engineer these design decisions from a simple study, so perhaps more advanced studies should be conduct at a larger scale? -- Why though?

%%John add conclusion ideas here
We were correct with the majority of our categorisations. The ones we did get wrong were because we did not think of it from specific points of view. This probably means that it's possible to reverse engineer to some extent, but not completely (Which is probably the answer most people would expect).

Considering the Ecosystem and considering it as a whole when designing the API. She does not think that they did take it into consideration at all. They had not thought about them when designing the APIs. She does think about who is going to use it and how but nothing in regards to how it affects an ecosystem as a whole. Things like allowing embedded web pages for the ACAP allows users to get more information from their system meaning they don’t need to ask for as much help and assistance. They usually integrate this with the VMS. Overall there was not much thought about ecosystem when the API was designed. She’s unsure if it’s one ecosystem or two. The network APIs and their API. Perhaps it is one ecosystem. (this is something Imed is looking at).
It seems that a focus on ecosystems might be starting to come through but that they already thought about them without calling them ecosystems. For example, her mentioning that they already did think about the users of the API and how they would be using it gives a slight clue that they do already think about the wider audience of their API.

%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close! <---- This could be done in conclusion when we discuss how it contribues to academia (i.e. say it enforces previous studies blabla)

%%William add conclusion ideas here
It's interesting that the partners have mentioned that they want more frequent updates... maybe API developers should be less afraid of updating them? 
That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
-Relate to 80% refactorings paper and say that we found different results
*This is an interesting note if we want to compare platform APIs and library APIs to say that functionality changes more often in platform APIs for example

%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!

>>>>

1. Small intro which: Summarises the findings of the discussion

2. Conclusions/outcomes:
Industry
Have a more structured feedback loop (include users) this can be future work too
              Greater emphasis should be placed upon communicating with the end users / application developers. They should probably improve their feedback system to get more feedback from the API users.
              Include more scientific theories
              --> consider ecosystem stuff

Academia
Some laws dont apply. Propose a new version of the law.
Interesting that hardware did not drive change. This is cool cuz it means hardware apis can be generalised to any type of api.
Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies
%%William add conclusion ideas here
That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
       MAke a study which looks the quality of applications before and after api changes have been introduced

3. Future work: Summarise what the next steps could be.
Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
       -->Suggest a similar study which looks at business factors

Random tips n trickz:
       Look up the papers from the conference (especially regarding the discussion/conclusion)
       discussion = revisiting research questions (and maybe structuring around industry/academia)
       conclusion = summary part, main final points and future work
